Issues with Dynamical Measurements Across the Disk

### 2019-02-15 paper/ms.tex
Add additional complications to midplane meas.

It is important for us to emphasize that when we state our local Galactic
midplane may be erroneous, we do not mean that past measurements/estimates of
it are wrong. Rather, what we mean is that it may vary from the local midplane
at other points in the Galaxy. In the face of {\em Gaia} DR2 (and soon DR3/4),
this may be an important effect to consider when performing dynamical
modelling across large distances.

>>>>

Our main point is that the local midplane varies between different points in
the Galaxy. This is a different statement than that our measurements of the
local midplane are erroneous. Indeed, the local midplane has recently been
measured to a claimed high level of precision, setting $z_{\odot} = 20.8 \pm
0.3\,\pc$ \citep{2019MNRAS.482.1417B}. However, we also do not mean to say
that determinations of the local midplane are perfect, since midplane
measurements from H~\textsc{ii} regions place $z_{\odot} \sim 5-10\,\pc$. An
additional complication is the fact that non-zero Solar heights induce a tilt
in the Galactic midplane \citep{2014ApJ...797...53G,2016ARAA..54..529B}.
